---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

<!-- badges: start -->
<!-- badges: end -->

# Template for parametrised reporting at INS

This repo holds a draft version for parametrised reports in Rmarkdown.  

Parameter features (the things that can be changed) include for now:  

 - center (level 1, level 2) 
 - language (allows for reporting in several languages for same center, important for bilingual cities)
 - restrict_level (if pct-agreement per answer should be restricted if less than X answers were given per group to protect respondents). 
 
 Other features include:  
 
 - Logo in header 
 - inclusion of Cover page from external pdfs 
 - switch from `rmarkdown::pdf_document` to `bookdown::pdf_document2`allows cross-platform editing (windows, mac and linux users) without the encoding-snafu  
 
 
 ## How to use it? 
 
 The easiest is to fork/clone or download this repo and start working locally. 
 
 ## How does it work?  
 
 *section is work in progress*
 
 This graph provides a general overview:
 
```{r, fig.align="center", fig.cap=c("Caption"), echo=FALSE}
knitr::include_graphics(here::here("vignettes/graph_tmpls-report.pdf"))
```
 
 ## Contributions welcome 👋
 
 Have an idea for the better? File an issue or start a PR - thanks. 
